### 2020-01-07 paper7/article.tex
starting ns-i

\item Contact force (acting on each overlapping pair $i,j$)
  \begin{subequations}
    \begin{equation} 
      \begin{aligned}
        {\bm F}^C_{i,j} = -k_n {\bm h}_{ij}  - \gamma_n \mathbb{P}_n({\bm u}_i-{\bm u}_j) - k_t {\bm \xi}_{ij},
      \end{aligned}
      \label{col F}
    \end{equation}
    \begin{equation} 
      \begin{aligned}
        {\bm F}^C_{j,i} = - {\bm F}^C_{i,j},  \quad \textrm{with} \quad 
        \abs{k_t {\bm \xi}_{ij}} \leq 
        \mu_c \abs{k_n {\bm h}_{ij}  + \gamma_n \mathbb{P}_n ({\bm u}_i-{\bm u}_j) },
      \end{aligned}
      \label{col F 2}
    \end{equation}
    \begin{equation} 
      \begin{aligned}
        {\bm T}^C_{i,j} = a_{i} k_t ({\bm n}_{ij} \times {\bm \xi}_{ij}),
      \end{aligned}
    \end{equation}
    \begin{equation} 
      \begin{aligned}
        {\bm T}^C_{j,i} = a_{j} k_t ({\bm n}_{ij} \times {\bm \xi}_{ij}).
      \end{aligned}
    \end{equation}
  \end{subequations}
  where ${\bm h}_{ij}=h_{ij}{\bm n}_{ij}$ denotes the signed normal surface gap between particles $i$ and $j$ (negative when overlapping), ${\bm \xi}_{ij}$ the signed tangential stretch (see Appendix \ref{app: tang stretch} for definition), $k_n$ the normal spring constant, $\gamma_n$ the damping constant, $k_t$ the tangential spring constant, and $\mu_c$ the friction coefficient. The condition in Eq.\ \eqref{col F 2} states the Coulomb's law of friction.

>>>>

\item Contact force (acting on each overlapping pair $i,j$)
  \begin{subequations}
    \begin{equation} 
      \begin{aligned}
        {\bm F}^C_{i,j} = -k_n {\bm h}_{ij}  - \gamma_n \mathbb{P}_n({\bm u}_i-{\bm u}_j) - k_t {\bm \xi}_{ij},
      \end{aligned}
      \label{col F}
    \end{equation}
    \begin{equation} 
      \begin{aligned}
        {\bm F}^C_{j,i} = - {\bm F}^C_{i,j},  \quad \textrm{with} \quad 
        \abs{k_t {\bm \xi}_{ij}} \leq 
        \mu_c \abs{k_n {\bm h}_{ij}  + \gamma_n \mathbb{P}_n ({\bm u}_i-{\bm u}_j) },
      \end{aligned}
      \label{col F 2}
    \end{equation}
    \begin{equation} 
      \begin{aligned}
        {\bm T}^C_{i,j} = a_{i} k_t ({\bm n}_{ij} \times {\bm \xi}_{ij}),
      \end{aligned}
    \end{equation}
    \begin{equation} 
      \begin{aligned}
        {\bm T}^C_{j,i} = a_{j} k_t ({\bm n}_{ij} \times {\bm \xi}_{ij}).
      \end{aligned}
    \end{equation}
  \end{subequations}
  where ${\bm h}_{ij}=h_{ij}{\bm n}_{ij}$ denotes the signed normal surface gap between particles $i$ and $j$ (positive when overlapping), ${\bm \xi}_{ij}$ the signed tangential stretch (see Appendix \ref{app: tang stretch} for definition), $k_n$ the normal spring constant, $\gamma_n$ the damping constant, $k_t$ the tangential spring constant, and $\mu_c$ the friction coefficient. The condition in Eq.\ \eqref{col F 2} states the Coulomb's law of friction.
